---
title: "NHSDataDictionaRy - Candidate Notebook"
author: "Gary Hutson"
date: "29/10/2021"
output: 
  html_document:
    toc: true
    toc_float: true
  
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(NHSDataDictionaRy)
library(ggplot2)
library(plotly)
library(purrr)
```

This is a notebook to support the NHSDataDictionaRy workshop. 



# Working with the nhs_data_elements() function

```{r nhs_data_elems}
# Your code here





```


# Scraping with the in built functionality in TableR

```{r scraping_in_earnest}
#Your code here






```

# Checking NHS website to validate
Tutor lead session of checking the elements on the website to make sure what we have scraped is correct.


# Task 1 - Have a go at scraping some contents from the website
Have a go at scraping some text from the website. Code below:

```{r candidate_scraping_nhs_data_dict}
# Your code 




```

# Quicker way to retrieve NHS Data Lookups with nhs_tableR

```{r working with nhs_table_r}
# Your code here








```


# Generating lookup data 

```{r generating_lookup_data}
# Your code here






```


# Using lookup data to join to lookup item retrieved

```{r using_lookup_data}
# Your code here






```


# Task 2 - Join the generated data to Main Specialty Code

```{r main_specialty_code}
# Your code here






```


# Wider use cases for scraping tool


# Case 1

```{r case_1}
# Your code here





```


# Task 3 - Have a go at scraping an HTML table

```{r your_code_here_task3}





```



# Scraping text from websites

```{r scraping_text_code_together}
#Your code here









```


# Task 4 - Scraping other pages

```{r scraping_text_your_turn}
# Your code here




```


# Capstone Project - Code Together

```{r capstone_project}
# Your code here















```




